Symmetric Peer-to-Peer Applications

### 2022-09-13 tpd-22.tex
...

In this section, we evaluate if (and to what extent) our design meets its goals
to ensure that all peers (a) meet event deadlines, (b) advance in sync in real
time, and (c) can leave and join the network and remain symmetric.
%
We simulate an application varying the network topology, latency, and churn, as
well as the frequency and deadlines of events.
%
We then measure (a) the recurrence of time travels, (b) the real-time pace of
peers, and (c) the correctness of unstable peers, such that they validate our
goals above, respectively.

Regarding (a), if a peer experiences a time travel, it means that it received
an event after its deadline.
We count all time travel occurrences during the simulation.
%
Regarding (b), we use an absolute simulation clock to track, in real time, the
execution pace of each peer in comparison to a reference peer most advanced in
time.
%
Regarding (c), we designate some peers to leave and join the network
periodically to assert that they catch up with the other peers in real time.

@@

Figure~\ref{TODO} results...
- colors indicate feasibility
%
We now detail how we instrument the middleware implementation to measure the
properties above:
%
\begin{enumerate}
%
\item \textbf{Recurrence of time travels:}
Every time a peer is ahead of time and needs to travel back, we output its id
and how much ticks it needs to travel back.
At the end, we measure the percentage of the sum of all time travel ticks over
the total simulation ticks (\code{TODO} in Figure~\ref{TODO}).
As an example, if all peers sum $1000$ time travel ticks over $100k$
accumulated simulation ticks, then the final measure is $1\%$.
%
\item \textbf{Real-time pace of peers:}
Every time a peer receives \code{SYNC} packets and is behind, we output its id
and how much ticks it needs to fast forward.
At the end, we measure the percentage of the sum of all forward ticks over the
total simulation ticks (\code{TODO} in Figure~\ref{TODO}).
As an example, if all peers sum $1000$ forward ticks over $100k$ accumulated
simulation ticks, then the final measure is $1\%$.
%
We also start each peer with a random delay of up to $10s$ to force a time
mismatch.
%
Each peer outputs its current tick continuously, allowing us to compare them
in the shared timeline.
Each time we see a greater tick never seen in the timeline before, we count
smaller ticks from other peers (considering latency), which would constitute
time violations (\code{TODO} in Figure~\ref{TODO}).
We expect this counter to be close to zero considering the whole execution.
\item \textbf{Correctness of unstable peers:}
- state (even for stable peers)
- time
%
\end{enumerate}

>>>>

In this section, we evaluate if (and to what extent) our design meets its goals
to ensure that all peers (a) meet event deadlines, (b) advance in sync in real
time, and (c) can leave and join the network and remain symmetric.
%
We simulate an application varying the network topology, latency, and churn, as
well as the frequency and deadlines of events.
%
We then measure (a) the recurrence of time travels, (b) the real-time pace of
peers, and (c) the recoverability from churns, such that they validate our
goals above, respectively.

Regarding (a), if a peer experiences a time travel, it means that it received
an event after its deadline.
We count all time travel occurrences during the simulation.
%
Regarding (b), we use an absolute simulation clock to track, in real time, the
execution pace of each peer in comparison to a reference peer most advanced in
time.
%
Regarding (c), we designate some peers to leave and join the network
periodically, possibly creating partitions, to assert that they all catch up in
real time.

@@

Figure~\ref{TODO} results...
- colors indicate feasibility
%
We now detail how we instrument the middleware implementation to measure the
properties above:
%
\begin{enumerate}
%
\item \textbf{Recurrence of time travels:}
Every time a peer is ahead of time and needs to travel back, we output its id
and how much ticks it needs to travel back.
At the end, we measure the percentage of the sum of all time travel ticks over
the total simulation ticks (\code{TODO} in Figure~\ref{TODO}).
As an example, if all peers sum $1000$ time travel ticks over $100k$
accumulated simulation ticks, then the final measure is $1\%$.
%
\item \textbf{Real-time pace of peers:}
Every time a peer receives \code{SYNC} packets and is behind, we output its id
and how much ticks it needs to fast forward.
At the end, we measure the percentage of the sum of all forward ticks over the
total simulation ticks (\code{TODO} in Figure~\ref{TODO}).
As an example, if all peers sum $1000$ forward ticks over $100k$ accumulated
simulation ticks, then the final measure is $1\%$.
%
We also start each peer with a random delay of up to $10s$ to force a time
mismatch.
%
Each peer outputs its current tick continuously, allowing us to compare them
in the shared timeline.
Each time we see a greater tick never seen in the timeline before, we count
smaller ticks from other peers (considering latency), which would constitute
time violations (\code{TODO} in Figure~\ref{TODO}).
We expect this counter to be close to zero even considering the whole
simulation.
%
\item \textbf{Correctness of unstable peers:}
- state (even for stable peers)
- time
- remove 13 (nao partition) e 10 (partition)
- qto tempo leva para sync
%
\end{enumerate}
